Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2020-02-01 doc/Paper/main.tex
Spell check.

      The resulting power spectrum measurements are shown in Figure \ref{fig:cls_summary} as dark green circles with error bars (hollow blue circles show the the absolute value of negative data). In all cases, we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a gray solid line in the auto-correlations. As described in Section \ref{ssec:methods.cell}, after deprojecting a set of contaminant templates, the power spectra estimated from the projected maps must be corrected for a bias caused by the loss of modes due to deprojection. This bias is also shown as a pink solid line in Figure \ref{fig:cls_summary}, where the dashed parts show the absolute value of the bias when it is negative. This bias is always at least a factor $\sim5$ smaller than the measured power spectra, and is most relevant on large scales. The semi-transparent gray bands in the figure cover the range of scales excluded from our analysis (described in Section \ref{ssec:methods.constr}). Unless otherwise stated, in what follows all our results will not include any of these data.

@@

      The positive side of the enhanced sensitivity of galaxy clustering to photometric redshift uncertainties compared to cosmic shear is the possibility of using clustering measurements to self-calibrate some of these uncertainties. As an example, our analysis hints towards a consistently positive value of the relative shift parameters $\Delta z_i-\Delta z_j,\,i>j$ (see e.g. Figs. \ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e. the different bins are more widely separated than their fiducial distributions assume. Since the amplitude of the cosmic shear signal increases towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions). Although the data analysed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
          \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
          \label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
        \end{center}
      \end{figure}

@@

  In a simplified model, let us assume that galaxies can be separated into discrete types labelled by an index $\alpha$. If we want to compute the value of a given quantity $Q$ in a pixel $p$ by averaging over all galaxies in that pixel, the result is:
  \begin{equation}
    \bar{Q}_p = \frac{\sum_\alpha N_{\alpha,p}Q_{\alpha,p}}{\sum_\alpha N_{\alpha,p}},
  \end{equation}
  where $N_{\alpha,p}$ is the number of galaxies of type $\alpha$ in pixel $p$, and $Q_{\alpha,p}$ is the value of $Q$ for those galaxies. Expanding $N_{\alpha,p}=\bar{N}_\alpha(1+\delta_{\alpha,p})$, where $\bar{N}_\alpha$ is the average number of galaxies of type $\alpha$ per pixel, and $\delta_{\alpha,p}$ is their overdensity, we obtain:
  \begin{align}\nonumber
    \bar{Q}_p&=\frac{\langle Q\rangle_p+\langle Q\delta\rangle_p}{1+\langle \delta\rangle_p}\\
             &\simeq\langle Q\rangle_p+\langle Q\delta\rangle_p-\langle Q\rangle_p\langle\delta\rangle_p+\mathcal{O}(\delta^2),
  \end{align}
  where we have defined $\langle f\rangle_p\equiv \sum_\alpha \bar{N}_\alpha f_{\alpha,p}/\sum_\alpha \bar{N}_\alpha$, and we have expanded to first order in $\delta$ in the second line. If $Q$ is constant across all galaxies, the second and third term in the second line cancel, and the resulting map would receive no noise from the inhomogeneous galaxy distribution ($\bar{Q}_p=\langle Q\rangle_p$) up to second order. This is however not the case for the flux errors used to estimate the depth map. Brighter sources have lower number densities (and therefore stronger shot-noise fluctuations), and also larger flux errors. Therefore, although the depth map estimated from mean galaxy flux errors is dominated by the large-scale depth fluctuations, the small-scale fluctuations trace the spatial distribution of the brightest galaxies, and thus correlate with the true galaxy distribution. This violates the core assumption of template deprojection (that the deprojected contaminant templates do not correlate with the true map fluctuations), and causes a bias in the estimated power spectrum.

>>>>

      The resulting power spectrum measurements \rev{for the four overlapping redshift bins illustrated in Fig.~\ref{fig:nzs}}, are shown in Figure \ref{fig:cls_summary} as dark green circles with error bars (hollow blue circles show the the absolute value of negative data). In all cases, we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a gray solid line in the auto-correlations. As described in Section \ref{ssec:methods.cell}, after deprojecting a set of contaminant templates, the power spectra estimated from the projected maps must be corrected for a bias caused by the loss of modes due to deprojection. This bias is also shown as a pink solid line in Figure \ref{fig:cls_summary}, where the dashed parts show the absolute value of the bias when it is negative. This bias is always at least a factor $\sim5$ smaller than the measured power spectra, and is most relevant on large scales. The semi-transparent gray bands in the figure cover the range of scales excluded from our analysis (described in Section \ref{ssec:methods.constr}). Unless otherwise stated, in what follows all our results will not include any of these data.

@@

      The positive side of the enhanced sensitivity of galaxy clustering to photometric redshift uncertainties compared to cosmic shear is the possibility of using clustering measurements to self-calibrate some of these uncertainties. As an example, our analysis hints towards a consistently positive value of the relative shift parameters $\Delta z_i-\Delta z_j,\,i>j$ (see e.g. Figs. \ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e. the different bins are more widely separated than their fiducial distributions assume. Since the amplitude of the cosmic shear signal increases towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions). Although the data analyzed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
          \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
          \label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
        \end{center}
      \end{figure}

@@

  In a simplified model, let us assume that galaxies can be separated into discrete types labeled by an index $\alpha$. If we want to compute the value of a given quantity $Q$ in a pixel $p$ by averaging over all galaxies in that pixel, the result is:
  \begin{equation}
    \bar{Q}_p = \frac{\sum_\alpha N_{\alpha,p}Q_{\alpha,p}}{\sum_\alpha N_{\alpha,p}},
  \end{equation}
  where $N_{\alpha,p}$ is the number of galaxies of type $\alpha$ in pixel $p$, and $Q_{\alpha,p}$ is the value of $Q$ for those galaxies. Expanding $N_{\alpha,p}=\bar{N}_\alpha(1+\delta_{\alpha,p})$, where $\bar{N}_\alpha$ is the average number of galaxies of type $\alpha$ per pixel, and $\delta_{\alpha,p}$ is their overdensity, we obtain:
  \begin{align}\nonumber
    \bar{Q}_p&=\frac{\langle Q\rangle_p+\langle Q\delta\rangle_p}{1+\langle \delta\rangle_p}\\
             &\simeq\langle Q\rangle_p+\langle Q\delta\rangle_p-\langle Q\rangle_p\langle\delta\rangle_p+\mathcal{O}(\delta^2),
  \end{align}
  where we have defined $\langle f\rangle_p\equiv \sum_\alpha \bar{N}_\alpha f_{\alpha,p}/\sum_\alpha \bar{N}_\alpha$, and we have expanded to first order in $\delta$ in the second line. If $Q$ is constant across all galaxies, the second and third term in the second line cancel, and the resulting map would receive no noise from the inhomogeneous galaxy distribution ($\bar{Q}_p=\langle Q\rangle_p$) up to second order. This is however not the case for the flux errors used to estimate the depth map. Brighter sources have lower number densities (and therefore stronger shot-noise fluctuations), and also larger flux errors. Therefore, although the depth map estimated from mean galaxy flux errors is dominated by the large-scale depth fluctuations, the small-scale fluctuations trace the spatial distribution of the brightest galaxies, and thus correlate with the true galaxy distribution. This violates the core assumption of template deprojection (that the deprojected contaminant templates do not correlate with the true map fluctuations), and causes a bias in the estimated power spectrum.
